site_map

### 2019-09-22 site_map.Rmd
Map update

```{r}
load("Data/site_list_sub.Rdata")
load("Data/africa_coast.RData")
xtable(site_list_sub, auto = TRUE)
west <- site_list_sub
west$coast <- "west" # Chnages wc to west

@@

>>>>

```{r}
load("Data/site_list_sub.Rdata")
load("Data/africa_coast.RData")
xtable(site_list_sub, auto = TRUE)
west <- site_list_sub[-5,]
west$coast <- "west" # Chnages wc to west

site_list_sub <- site_list_sub[-5,]

@@

site_list_sub <- site_list_sub[-5,]
